A tale of two cities: A GIS based data synthesis approach to understanding semantic decompositions of Twitter user locations

### 2016-10-17 semantic_decomposition_of_twitter_user_locations/paper.tex
Revert "hope it works"
This reverts commit 43218950806362a5c77e513fb4be43499ad56636.

\begin{document}
% \title{A data synthesis approach for semantic decompositions of Twitter user locations: A case study of geo-located Twitter data in Chicago}
\title{A tale of two cities: A GIS based data synthesis approach to understanding semantic decompositions of Twitter user locations}
\author{Junjun Yin}
\author{Shaowen Wang~\thanks{shaowen@illinois.edu}}
\affil[1]{Department of Geography and Geographic Information Science}
\affil[ ]{University of Illinois at Urbana-Champaign, IL, 61801, USA}
\affil[2]{CyberGIS Center for Advanced Digital and Spatial Studies}
\affil[3]{Department of Geography and Geographic Information Science}
\affil[4]{National Center for Supercomputing Applications}
\affil[ ]{University of Illinois at Urbana-Champaign, IL, 61801, USA}
\renewcommand\Authands{ and }
\maketitle

\section*{Abstract}
Semantic Trajectory Mining for Location Prediction

Today's pervasive Location Based Social Media provide abundant user-generated geographic information
In this paper, we present a geographical information system (GIS) based data synthesis approch to understanding semantic decompositions of Twitter user locations.
Specifically, we implemented a
This approach 
We analyzed the

>>>>

\begin{document}
% \title{A data synthesis approach for semantic decompositions of Twitter user locations: A case study of geo-located Twitter data in Chicago}
\title{A tale of two cities: A GIS based data synthesis approach to understanding semantic decompositions of Twitter user locations}
% \author~\thanks{yinjunjun@gmail.com]{Junjun Yin}
\author{Junjun Yin~\thanks{jyn@illinois.edu}}
\affil[1]{Department of Geography and Geographic Information Science}
\affil[ ]{University of Illinois at Urbana-Champaign, IL, 61801, USA}
\renewcommand\Authands{ and }
\maketitle

\section*{Abstract}
Today's pervasive Location Based Social Media provide abundant user-generated geographic information
In this paper, we present a geographical information system (GIS) based data synthesis approch to understanding semantic decompositions of Twitter user locations.
Specifically, we implemented a
This approach 
We analyzed the
